Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-21 paper.tex
Fancy sublabels

\begin{figure}[hbt!]
\includegraphics[width=0.495\textwidth]{experiments/start.eps}
\includegraphics[width=0.495\textwidth]{experiments/end.eps}
\caption{Comparison of \texttt{start\_X$_{LT}$} (left) and \texttt{end\_X$_{LT}$} (right) queries, with all variants}
\end{figure}

\begin{figure}[hbt!]
\includegraphics[width=0.495\textwidth]{experiments/xy0.eps}
\includegraphics[width=0.495\textwidth]{experiments/xy1.eps}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (left) and starting time (right) restrictions}
\end{figure}

\begin{figure}[hbt!]
\includegraphics[width=0.495\textwidth]{experiments/xy2.eps}
\includegraphics[width=0.495\textwidth]{experiments/xy3.eps}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (left) and starting time (right) restrictions with a fixed ending time restriction}
\end{figure}

>>>>

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy0.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy1.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions}
\end{figure}

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy2.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/xy3.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (a) and starting time (b) restrictions with a fixed ending time restriction}
\end{figure}
